Meta-analytic approaches and 'new' effect sizes to account for heterogeneous effects in comparative physiology

### 2021-06-14 MS/ms.Rmd
Adding some clarification

In the words of Gene Glass, arguably the father of meta-analysis: "Of course it mixes apples and oranges; in the study of fruit nothing else is sensible; comparing apples and oranges is the only endeavor worthy of true scientists; comparing apples to apples is trivial" [p.g., 224, @Glass2015]. We tend to agree, particularly in comparative physiology. By synthesizing diverse study outcomes, it allows us to not just report on overall effects, but understand critical features of the literature, study systems and approaches that can explain the diversity of effect outcomes observed. In doing so, it provides a richer set of conclusions that can draw attention to important sources of variability that might otherwise be overlooked. Having said that, it is still very improtant to understand the limitations and diversity of studies included within a meta-analysis. Answers to certain questions will inevitably depend on the homogeneity of effects being synthesized.

>>>>

In the words of Gene Glass, arguably the father of meta-analysis: "Of course it mixes apples and oranges; in the study of fruit nothing else is sensible; comparing apples and oranges is the only endeavor worthy of true scientists; comparing apples to apples is trivial" [p.g., 224, @Glass2015]. @Glass2015's intention was to simply highlight that whether comparing apples and oranges is a good idea simply boils down to the specific question of interest. If we are interested in gaining insight into 'fruit' then synthesising apples and oranges is a good idea. Instead, if we are intersted in generalising to apples only, then mixing fruit will not be ideal. We tend to agree with @Glass2015 and his sentiment is of particular relevance to comparative physiology. By synthesizing diverse study outcomes, it allows us to not just report on overall effects, but understand critical features of the literature, study systems and approaches that can explain the diversity of effect outcomes observed. In doing so, it provides a richer set of conclusions that can draw attention to important sources of variability that might have otherwise been overlooked. Having said that, it is still very important to understand the limitations and diversity of studies included within a meta-analysis. Answers to certain questions will inevitably depend on the homogeneity of effects being synthesized.
